Resolving the measurement uncertainty paradox in ecological management

### 2018-12-07 manuscripts/manuscript.Rmd
rebuild mansucript locally

```{r load_data, message=FALSE, warning=FALSE}
log_dir <- "../data/observe_harvest_recruit" # solution files here

@@

## Fig 5
ram_ex <- read_csv(file.path(log_dir, "../ram_ex/ram_ex.csv"))

>>>>

```{r load_data, message=FALSE, warning=FALSE}
log_dir <- "../data/appendixA" # solution files here

@@

## Fig 5
ram_ex <- read_csv(file.path("../data/appendixB/appendixB.csv"))
